### 2014-04-14 paper/exampleobjects.tex
fixing feedback

The models we used for the toys were downloaded from the  Thingiverse website. \bjoern{I thought the brain model came from Berkeley?} We then used \systemname to create the desired internal pipes. All components were fabricated on a Makerbot, support-free.  After printing, we injected copper paint (CuPro-Cote) into the interior pipes using a craft syringe.  This paint requires approximately 2 days to fully dry in this configuration (3mm diameter tubes, maximum tube length 10cm).  Our smart base is powered by an Arduino Uno running open-source SFCS code\footnote{\url{http://www.instructables.com/id/Touche-for-Arduino-Advanced-touch-sensing}}. \bjoern{If we don't have appendices, insert resistance measurement for this paint here.}

@@

\subsection{Custom Radio (open, threadable, endpoint)}
A custom radio (Figure \ref{fig:examples}c) shows how pipes can be used to integrate electronic components into the user-facing surface of an object. The radio includes a power and volume dial, and LED which goes on when the radio is on, and a tuner dial. An Arduino Pro Micro microcontroller, Si4703 FM tuner, and 6V (4xAA) power supply are embedded in the base of the radio. The sound is played through a single .5 Watt speaker. This shows a Midas-like \cite{Savage-midas} possibility : multiple terminals all routed back to a shared endpoint (in this case, the Arduino). \bjoern{last sentence is confusing. May not need Midas reference.}

@@

\subsection{Presence-aware Pen Holder (open, threadable, endpoint)}
Our presence-aware pen holder can distinguish which tool or tools a user has picked up (see Figure \ref{fig:examples}d).  Our pen holder uses a modification of the FlyEye technique described by Wimmer \cite{Wimmer-flyeye} in which an IR camera senses a user's grasp on an object, getting data from IR light transmitted on fiber optic cables.  We marry this technique here with the Sauron technique \cite{Savage-sauron}: instead of using mirrors to redirect light and motion sensing as Sauron does, we use fiber optic cables. \bjoern{I think people remember Sauron as being all about hollow objects and we use ray-tracing to know how reflected light will travel; using fiberoptics seems not that closely related, other than its use of optical sensors.}

@@

The maze is based on an SVG file we manually created and processed with our internal path routing tool.  We printed the maze on the Objet using a transparent material \bjoern{bottom doesn't look transparent. The final artifact was fabricated in two halves fastened together via glue, to allow removal of support material with a high-pressure water tool.  We plugged the ends of the tubes post-print with additional material to ensure the ball does not escape.

>>>>

The models we used for the boat was downloaded from Thingiverse, while the brain model came from researchers at one of our instutions. \valkyrie{how to phrase that?} We then used \systemname to create the desired internal pipes. All components were fabricated on a Makerbot, support-free.  After printing, we injected copper paint (CuPro-Cote) into the interior pipes using a craft syringe.  This paint requires approximately 2 days to fully dry in this configuration (3mm diameter tubes, maximum tube length 10cm).  The resistance of the paint in this configuation is approximately $2\Omega / inch.$  Our smart base is powered by an Arduino Uno running open-source SFCS code\footnote{\url{http://www.instructables.com/id/Touche-for-Arduino-Advanced-touch-sensing}}.

@@

\subsection{Custom Radio (open, threadable, endpoint)}
A custom radio (Figure \ref{fig:examples}c) shows how pipes can be used to integrate electronic components into the user-facing surface of an object. The radio includes a power and volume dial, and LED which goes on when the radio is on, and a tuner dial. An Arduino Pro Micro microcontroller, Si4703 FM tuner, and 6V (4xAA) power supply are embedded in the base of the radio. The sound is played through a single .5 Watt speaker. \valkyrie{Tovi, if you are thinking of a Midas reference here... can you help write it?}

@@

\subsection{Presence-aware Pen Holder (open, threadable, endpoint)}
Our presence-aware pen holder can distinguish which tool or tools a user has picked up (see Figure \ref{fig:examples}d).  Our pen holder uses a modification of the FlyEye technique described by Wimmer \cite{Wimmer-flyeye} in which an IR camera senses a user's grasp on an object, getting data from IR light transmitted on fiber optic cables.

@@

The maze is based on an SVG file we manually created and processed with our internal path routing tool.  We printed the maze on the Objet using a transparent material for the top and a black material for the bottom. The final artifact was fabricated in two halves fastened together via glue, to allow removal of support material with a high-pressure water tool.  We plugged the ends of the tubes post-print with additional material to ensure the ball does not escape.
